% --- WORK EXPERIENCE ---
% Using itemsep in the outer itemize to add a bit more space between job entries.
% Using topsep and itemsep in inner itemize for finer control of bullet point spacing.
\begin{itemize}[leftmargin=*, label={}, itemsep=0.1in]

    \item
    \textbf{Senior Software Developer Engineer in Testing (EN)} $|$ Willis Tower Watson $|$ Lima, Peru \hfill \textit{JUNE 2024 – PRESENT}
    \begin{itemize}[leftmargin=0.25in, label=\textbullet, topsep=0.05in, itemsep=0.02in]
        \cvitem{Serves as a full-time Tester for WTW - Extend Health, USA (Client), operating under the Scrum agile methodology.}
        \cvitem{Spearheads the analysis, review, and approval of test plans, E2E tests, Integration tests, and automated tests utilizing Selenium WebDriver, Zephyr, Azure DevOps, Cypress, Robot Framework, Playwright, and BrowserStack.}
        \cvitem{Commands the QA process, including test definition and the execution of automation testing across the entire environment. \textit{[Add a quantifiable achievement if possible, e.g., "Streamlined testing cycles by X\%"]}}
        \cvitem{\textbf{Key Technologies/Languages:} C\# with Selenium, JavaScript with Playwright, Python with Selenium.}
    \end{itemize}

    \item
    \textbf{Senior Consultant Automation Tester Engineer (EN)} $|$ Aurus Ti $|$ Lima, Peru \hfill \textit{MARCH 2023 – MAY 2024}
    \begin{itemize}[leftmargin=0.25in, label=\textbullet, topsep=0.05in, itemsep=0.02in]
        \cvitem{Operated as a contract Tester for Hastings Deerings - CAT, Australia (Client), adhering to the Scrum agile methodology.}
        \cvitem{Directed the analysis, review, and approval of test plans, E2E tests, and Integration tests; developed and executed automated tests using Selenium WebDriver, Karate, Jenkins, Serenity, Appium, Cypress, Playwright, and BrowserStack.}
        \cvitem{Ensured the quality of QA projects, proactively mitigating errors during CircleCI deployments and generating comprehensive reports in AllureTestOps. \textit{[Add a quantifiable achievement if possible, e.g., "Reduced post-deployment defects by Y\%"]}}
        \cvitem{\textbf{Key Technologies/Languages:} Java with Selenium \& Appium, C\# with Selenium, Python with Appium.}
    \end{itemize}

    \item
    \textbf{Automation Tester Engineer (EN)} $|$ Globant $|$ Lima, Peru \hfill \textit{JUNE 2023 – OCTOBER 2023}
    \begin{itemize}[leftmargin=0.25in, label=\textbullet, topsep=0.05in, itemsep=0.02in]
        \cvitem{Functioned as a Contractor QA Automation Tester for PWC - USA (Client) within a Scrum agile framework.}
        \cvitem{Led the analysis, review, and approval of test plans, E2E tests, and Integration tests; implemented automated tests using Cypress, Azure DevOps, TypeScript, NodeJS, and BrowserStack.}
        \cvitem{Pioneered the creation, enhancement, and deployment of a Proof of Concept for the “Tax \& Accounting Management Service” web platform.}
        \cvitem{\textbf{Key Technologies/Languages:} JavaScript with Playwright \& Cypress.}
    \end{itemize}

    \item
    \textbf{Automation Tester Engineer (EN)} $|$ Oktana $|$ Lima, Peru \hfill \textit{OCTOBER 2022 – FEBRUARY 2023}
    \begin{itemize}[leftmargin=0.25in, label=\textbullet, topsep=0.05in, itemsep=0.02in]
        \cvitem{Engaged as a full-time Tester for Slack / SalesForce - North America (Client) under the Scrum agile methodology (NDA).}
        \cvitem{Developed comprehensive test plans, E2E tests, and Integration tests; executed automated tests with Selenium WebDriver, Karate, Jenkins, Serenity, Appium (UIAutomator2), and conducted performance tests using JMeter and Postman.}
        \cvitem{Performed rigorous testing on Salesforce / Salesforce Lighting websites and conducted API Testing on Salesforce API Services.}
        \cvitem{\textbf{Key Technologies/Languages:} C\# with Selenium, JavaScript with Cypress, Python with BeautifulSoup.}
    \end{itemize}

    \item
    \textbf{Automation Tester (ES, EN)} $|$ NTT Data (Everis) $|$ Trujillo, Peru \hfill \textit{AUGUST 2021 – SEPTEMBER 2022}
    \begin{itemize}[leftmargin=0.25in, label=\textbullet, topsep=0.05in, itemsep=0.02in]
        \cvitem{Served as a full-time Tester for La Junta de Andalucía - Spain (Client) within a Scrum agile environment.}
        \cvitem{Architected test plans, E2E tests, and Integration tests; implemented automated tests using Selenium WebDriver, Robot Framework, Jenkins, Gherkin, JDBC, and Dedalow (proprietary software); executed performance tests with JMeter (Selenium integration) and Postman.}
        \cvitem{Delivered training on Query and API Automation using JDBC and REST Assured (Java).}
        \cvitem{Led an Automation Team of 4 junior testers in an outsourcing project.}
        \cvitem{Conducted professional profile analysis and technical interviews for recruitment.}
        \cvitem{\textbf{Key Technologies/Languages:} Java with Selenium, RestAssure \& Appium, Python for Performance Testing, C\# with Selenium.}
    \end{itemize}

    \item
    \textbf{QA Tester (ES)} $|$ Delaware Group $|$ Lima, Peru \hfill \textit{MARCH 2021 – AUGUST 2021}
    \begin{itemize}[leftmargin=0.25in, label=\textbullet, topsep=0.05in, itemsep=0.02in]
        \cvitem{Operated as a full-time Tester for Telefónica Movistar - Peru (Client) under the Scrum agile methodology.}
        \cvitem{Executed E2E tests, Integration tests, and automated tests using Selenium WebDriver, Postman, SoapUI, Android Studio, and Appium.}
        \cvitem{Conducted stress tests utilizing JMeter, Postman, CURL, and REST Assured.}
        \cvitem{\textbf{Key Technologies/Languages:} Java with Selenium.}
    \end{itemize}

    \item
    \textbf{Web Scraping \& Data Acquisition (ES, EN)} $|$ Directorate of Research, Development and Innovation of Data Science Research Peru $|$ Lima, Peru \hfill \textit{NOVEMBER 2020 – MARCH 2021}
    \begin{itemize}[leftmargin=0.25in, label=\textbullet, topsep=0.05in, itemsep=0.02in]
        \cvitem{Contributed as a part-time specialist under the Kanban agile methodology.}
        \cvitem{Engineered solutions for gathering data from government websites using BeautifulSoup4 and Selenium WebDriver.}
        \cvitem{Managed relational database reconstruction (PostgreSQL, SQL Server) and ETL Operations.}
        \cvitem{\textbf{Key Technologies/Languages:} Python with Selenium \& BeautifulSoup.}
    \end{itemize}

    \item
    \textbf{Freelancer Full Stack Web DevOps (ES, EN, PT)} $|$ Peru \hfill \textit{MAY 2019 – PRESENT}
    \begin{itemize}[leftmargin=0.25in, label=\textbullet, topsep=0.05in, itemsep=0.02in]
        \cvitem{Provides part-time freelance development and sysadmin services for small to medium enterprises.}
        \cvitem{Develops solutions using JavaScript, Python, Bash, Ruby, PHP on Cloud platforms (AWS \& GCloud) with Linux VMs.}
        \cvitem{Manages web server setup, web page deployment, routing, and web hosting/domain configuration.}
        \cvitem{\textbf{Key Technologies/Languages:} JavaScript, Python, Ruby, PHP, Bash.}
    \end{itemize}
\end{itemize}
